---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub

We will subset the data by sex to see if the drug is sex specific.


# Atriplavast

We will subset the data by sex to see if the drug is sex specific.



# abacavirinol

```{r}
abacall <- xtabs(~infected+group,data=abacavirinol)
barchartGC(abacall,type="percent")
```

we can see in this barchart that the drug prevented a bit of people from contracting aids, but it is not an effective drug when looking at both genders together.

```{r}
rowPerc(abacall)
colPerc(abacall)
```

we can see that the numbers are almost exact when it comes to comparing those who took the drug and those who didnt.

```{r}
chisqtestGC(abacall,graph=TRUE)
```
 the pvalue is .89 meaning that both datas are very similar. this tells us that the drug did little difference. uneffectine in other words.

We will subset the data by sex to see if the drug is sex specific.

##Male

```{r}
abacmale<- filter(abacavirinol,sex=="M")
tababacmale <- xtabs(~infected+group,data=abacmale)
barchartGC(tababacmale,type="percent")
```

it looks like similar to the atriplavast test, this drug increases the chances of getting aids except this time for males.

```{r}
rowPerc(tababacmale)
colPerc(tababacmale)
```

as we can see, just like the atriplavast, the number of males who took the drug and got aids increased by 2%

```{r}
chisqtestGC(tababacmale,graph=TRUE)
```

we were given a pvalue of .09 meaning that there was a big difference between those who didnt take the drug vs those who did. although the results were negative, the drug did have an effect.

##Females

```{r}
abacfemale <- filter(abacavirinol,sex=="F")
tababacfemale <- xtabs(~infected+group,data=abacfemale)
barchartGC(tababacfemale,type="percent")
```

it looks like opposite of the male barchart, this drug has positive results on females. it seem that less females got aids when taking the drug.

```{r}
rowPerc(tababacfemale)
colPerc(tababacfemale)
```

although its not as effective as it should idealy be, it is the most effective on Females of the three drugs we have looked at in this study. there were 2% less females with aids

```{r}
chisqtestGC(tababacfemale,graph=TRUE)
```

the pvalue of 0.02 tells us that the drug made a big change. the big change being that drug does actually prevent aids in females.