---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Thailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub

```{r}
tabinfgroall<- xtabs(~infected+group,data=Genvoyabub)
barchartGC(tabinfgroall,type="percent")
```
  
This barchart shows us that the those who didn get aids were slightly less likely to have aids by taking the drug, and there are less people who got aids and took the drug, than those who got aids and didnt take the drug.

```{r}
rowPerc(tabinfgroall)
colPerc(tabinfgroall)
```

between both genders, the druf had an effect, but it was a very small effect. the drug only prevented .15% of people from getting aids.

```{r}
chisqtestGC(tabinfgroall,graph=TRUE)
```

the Pvalue of 0.57 means that you have a 57% chance of ending up with the same results. that is a very high pvalue and signifies that the study and results are fairly consistent.

We will subset the data by sex to see if the drug is sex specific

##Males
```{r}
infgromale<- filter(Genvoyabub,sex=="M")
tabinfgromale<- xtabs(~infected+group,data=infgromale)
barchartGC(tabinfgromale,type="percent")
```
  
This barchart shows us the same results as the previous chart, but with less change meaning that it isnt very effective on males.

```{r}
rowPerc(tabinfgromale)
colPerc(tabinfgromale)
```

The results of those who took the placebo and those who took the drug was almost identical meaning that taking the drug had no significant difference. atleast on males.

```{r}
chisqtestGC(tabinfgromale,graph=TRUE)
```
  
the Pvalue in this chi square test is 1 meaning that we definitely cannot reject that the drug has effects on males.

##Females

```{r}
infgrofemale<- filter(Genvoyabub,sex=="F")
tabinfgrofemale<- xtabs(~infected+group,data=infgrofemale)
barchartGC(tabinfgrofemale,type="percent")
```
  
This barchart shows us the same results as the pevious two barcharts, but with more effect meaning that this drug is more effective on females than it is on males.

```{r}
rowPerc(tabinfgrofemale)
colPerc(tabinfgrofemale)
```

the effect the drug had on females is not much, but we can see that it had more effect on females than it did on males.

```{r}
chisqtestGC(tabinfgrofemale, graph=TRUE)
```
  
the pvalue given to us is 0.50 meaning you will achieve the same results half of the time. it is the lowest of the 3, but it is still a high probability. This shows that we cannot disprove that the drug has an effect on females. infact ths drug does more effect on felames than males.

# Atriplavast
```{r}
atriall <- xtabs(~infected+group,data=Atriplavast)
barchartGC(atriall,type="percent")
```
we can see in the barchart that there is actually a pretty significant difference in the results of those who took the drug vs those who didnt.

```{r}
rowPerc(atriall)
colPerc(atriall)
```

as you can see in the coloumn percent chart, the drug prevented a little over one percent of the people in contracting aids.

```{r}
chisqtestGC(atriall,graph=TRUE)
```

The p-value of 0.06 confirms that there is a significant difference and the drug definitely works because the lower the pvalue, the more difference in the data.

We will subset the data by sex to see if the drug is sex specific.

##Males

```{r}
atrimale <- filter(Atriplavast, sex=="M")
tabatrimale <- xtabs(~infected+group,data=atrimale)
barchartGC(tabatrimale,type="percent")
```

this male barchart seems to have a bigger difference than the barchart with both genders meaning that the drug must be more effective on males.

```{r}
rowPerc(tabatrimale)
colPerc(tabatrimale)
```

as expected, the drug pervented a whole 5% of males from contracting aids. the Drug did have a large effect on males.

```{r}
chisqtestGC(tabatrimale,graph=TRUE)
```

the Pvalue given to us was 0 meaning that the results from those who took the placebo and those who took the drug had no similarities therefore, it is very obvious that the drug did have a big effect on males.

##Females

```{r}
atrifemale <- filter(Atriplavast, sex=="F")
tabatrifemale <- xtabs(~infected+group,data=atrifemale)
barchartGC(tabatrifemale,type="percent")
```

From what the barchart shows us, it looks like the drug actually increased the chances of females getting aids.

```{r}
rowPerc(tabatrifemale)
colPerc(tabatrifemale)
```

this chart gives us a clearer understanding on what the differences were, and it turns out that the number of females with aids increased by 2% when they took the drug.

```{r}
chisqtestGC(tabatrifemale,graph=TRUE)
```

we can see that our pvalue is extremely small at 0.006 this is because the drug worked in a negative way. instead of preventing aids, it increased the chances of females getting aids. it worked well on Males, but Females should definitely stay away from this one.

# abacavirinol

```{r}
abacall <- xtabs(~infected+group,data=abacavirinol)
barchartGC(abacall,type="percent")
```

we can see in this barchart that the drug prevented a bit of people from contracting aids, but it is not an effective drug when looking at both genders together.

```{r}
rowPerc(abacall)
colPerc(abacall)
```

we can see that the numbers are almost exact when it comes to comparing those who took the drug and those who didnt.

```{r}
chisqtestGC(abacall,graph=TRUE)
```
 the pvalue is .89 meaning that both datas are very similar. this tells us that the drug did little difference. uneffectine in other words.

We will subset the data by sex to see if the drug is sex specific.

##Male

```{r}
abacmale<- filter(abacavirinol,sex=="M")
tababacmale <- xtabs(~infected+group,data=abacmale)
barchartGC(tababacmale,type="percent")
```

it looks like similar to the atriplavast test, this drug increases the chances of getting aids except this time for males.

```{r}
rowPerc(tababacmale)
colPerc(tababacmale)
```

as we can see, just like the atriplavast, the number of males who took the drug and got aids increased by 2%

```{r}
chisqtestGC(tababacmale,graph=TRUE)
```

we were given a pvalue of .09 meaning that there was a big difference between those who didnt take the drug vs those who did. although the results were negative, the drug did have an effect.

##Females

```{r}
abacfemale <- filter(abacavirinol,sex=="F")
tababacfemale <- xtabs(~infected+group,data=abacfemale)
barchartGC(tababacfemale,type="percent")
```

it looks like opposite of the male barchart, this drug has positive results on females. it seem that less females got aids when taking the drug.

```{r}
rowPerc(tababacfemale)
colPerc(tababacfemale)
```

although its not as effective as it should idealy be, it is the most effective on Females of the three drugs we have looked at in this study. there were 2% less females with aids

```{r}
chisqtestGC(tababacfemale,graph=TRUE)
```

the pvalue of 0.02 tells us that the drug made a big change. the big change being that drug does actually prevent aids in females.

# Conclusion

What we have learned is that that different drugs work better or worse depending on which gender it is used on. the Genvoyabub had an insignificant difference on either gender making it petty much useless. the Atriplavast had a good effect on males reducing their chance of contracting aids, but it actually increased the females chance of getting aids. Abacavirinol had a bad effect on males increasing their chance of getting aids, but it worked well on females. so males should take Atriplavast, and Females should take Abacavirinol.

  




