---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub

We will subset the data by sex to see if the drug is sex specific.

```{r}
tabinfgroall<- xtabs(~infected+group,data=Genvoyabub)
barchartGC(tabinfgroall,type="percent")
```
  
This barchart shows us that the those who didn get aids were slightly less likely to have aids by taking the drug, and there are less people who got aids and took the drug, than those who got aids and didnt take the drug.

```{r}
rowPerc(tabinfgroall)
colPerc(tabinfgroall)
```

between both genders, the druf had an effect, but it was a very small effect. the drug only prevented .15% of people from getting aids.

```{r}
chisqtestGC(tabinfgroall,graph=TRUE)
```

the Pvalue of 0.57 means that you have a 57% chance of ending up with the same results. that is a very high pvalue and signifies that the study and results are fairly consistent.

##Males Genvoyabub
```{r}
infgromale<- filter(Genvoyabub,sex=="M")
tabinfgromale<- xtabs(~infected+group,data=infgromale)
barchartGC(tabinfgromale,type="percent")
```
  
This barchart shows us the same results as the previous chart, but with less change meaning that it isnt very effective on males.

```{r}
rowPerc(tabinfgromale)
colPerc(tabinfgromale)
```

The results of those who took the placebo and those who took the drug was almost identical meaning that taking the drug had no significant difference. atleast on males.

```{r}
chisqtestGC(tabinfgromale,graph=TRUE)
```
  
the Pvalue in this chi square test is 1 meaning that we definitely cannot reject that the drug has effects on males.

##Females Genvoyabub

```{r}
infgrofemale<- filter(Genvoyabub,sex=="F")
tabinfgrofemale<- xtabs(~infected+group,data=infgrofemale)
barchartGC(tabinfgrofemale,type="percent")
```
  
  This barchart shows us the same results as the pevious two barcharts, but with more effect meaning that this drug is more effective on females than it is on males.

```{r}
rowPerc(tabinfgrofemale)
colPerc(tabinfgrofemale)
```

the effect the drug had on females is not much, but we can see that it had more effect on females than it did on males.

```{r}
chisqtestGC(tabinfgrofemale, graph=TRUE)
```
  
the pvalue given to us is 0.50 meaning you will achieve the same results half of the time. it is the lowest of the 3, but it is still a high probability. This shows that we cannot disprove that the drug has an effect on females. infact ths drug does more effect on felames than males.

# Atriplavast

We will subset the data by sex to see if the drug is sex specific.



# abacavirinol

We will subset the data by sex to see if the drug is sex specific.






